The \dealii{} Library, Version 9.0

### 2018-04-05 9.0/paper.tex
Augment description of some of the major changes

\item
  C++11 is now required and used in many places, move semantics, ... (...)

@@

\item
  Increase support for dense solvers (LAPACK changes and new ScaLAPACK
  interface).

@@

\item
  Support for Particles

\item
  Support for automatically differentiable numbers

@@

\item
  Support for Nanoflann

\item
  Support for Assimp

\item
  Initial support for GMHS

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{2}
\begin{itemize}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item Threading Building Blocks \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

>>>>

\item
  C++11 is now required and used in many places. For performance reason,
  move semantics is used when possible and in many places, \texttt{emplace\_back} 
  replaces \texttt{push\_back()}. C-style raw pointers have been replaced by
  \texttt{shared\_ptr} and \texttt{unique\_ptr} to avoid the risk of memory leak.
  Private constructors have been removed and instead were delete. clang-tidy is
  now being used to ensure the quality of the code.

@@

\item
  Increased support for dense solvers (LAPACK changes and new ScaLAPACK
  interface).

@@

\item
  A dedicated particles module has been created to provide support for the
  storage of particles and their properties. This module provides a base class
  \texttt{Particles} which represents a particle with position, an ID number and
  a variable number of properties. It also provides a \texttt{ParticleHandler}
  class that manages the storage and handling of particles. This class
  distributes the particles in distributed domains (these are the only domains
  supported by this class so far)

\item
  A dedicated differentiation module had been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivates of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.

@@

\item
  Support for the nanoflann library. nanoflann is a library for building
  KD-trees of datasets and for the fast querying of closest neighbors in
  KD-trees. nanoflann is used to speed up the search of the p nearest neighbors
  of a given point, or searching the points that fall within a radius of a
  target point.

\item
  Support for the Open Asset Import Library (Assimp). Assimp can be used to read
  about 40 different 3D graphics formats. A subset of these formats can be used
  to generate two-dimensional meshes possibly embedded in a three-dimensional
  space.

\item
  Initial support for Gmsh

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{2}
\begin{itemize}
\item Adol-c \cite{adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item Threading Building Blocks \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.
